Usable Functional Reactive Programming with Slipstreams

### 2014-03-06 paper.tex
Changes and a bib

\documentclass[twocolumn]{paper}
\usepackage{authblk}
\usepackage{listings}
\usepackage{amsmath}
\lstset{language=Haskell}

@@

\begin{document}
\maketitle
\section{Abstract}
We give a definition of \textit{Functional Reactive Programming} (FRP) for use in a javascript based environment that allows for the manipulation of DOM elements and remote servers through the use of sinks and sources in the network. There is also an implementation of the FRP network using a DSL to specify the varying layers of the network, this allows a programmer to easily design networks to accomplish tasks by simply specifying the layers and how the layers interact. Our implementation builds on previous ones by being more practical, the DSL arises naturally from our definition of FRP and the DSL is simple to use and requires no knowledge of the underlying FRP concepts. End sales pitch.

@@

\item[space-time leak] In a functional reactive service any particular element can depend on values that are far in the past. Clearly the longer the program is executing, the longer the history of events, or the longer the stream is. A longer stream takes up more memory and can cause slowdown if the stream is not trimmed after a certain point. Typically a garbage collection service of some kind is used to clean up old events that no longer being depended on. This is analogous to a memory leak in imperative programming. The value is said to be a space-time leak if it is unnessisarly being used for computations when it will have no affect on any current elements.
\end{description}
\section{Related work}
\subsection{High order streams}
\cite{streams}
\section{Future work}
Probably some since we want to keep working on things. I bet it will have to do with extending the language definition and possibly defining streams better.
\begin{thebibliography}{9}
  \bibitem{wormholes}
    Daniel Winograd-Cort, Paul Hudak.
    \emph{Wormholes: Introducing Effects to FRP}
    Yale University

  \bibitem{fran}
    Conal Elliott and Paul Hudak. 
    Functional reactive animation.
    \emph{In International Conference on Functional Programming},
    June 1997, pages 263-273.

\bibitem{streams}
  Gergely Patai.
  Ecient and Compositional Higher-Order Streams.
  Budapest University of Technology and Economics, Budapest, Hungary

\end{thebibliography}
\end{document}

>>>>

\documentclass[twocolumn]{paper}
\usepackage{authblk}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{cite}
\usepackage[margin=1.0in]{geometry}
\lstset{language=Haskell}

@@

\begin{document}
\maketitle

\section{Abstract}
We give a definition of \textit{Functional Reactive Programming} (FRP) for use in a javascript based environment that allows for the manipulation of DOM elements and remote servers through the use of sinks and sources in the network. There is also an implementation of the FRP network using a DSL to specify the varying layers of the network, this allows a programmer to easily design networks to accomplish tasks by simply specifying the layers and how the layers interact. Our implementation builds on previous ones by being more practical, the DSL arises naturally from our definition of FRP and the DSL is simple to use and requires no knowledge of the underlying FRP concepts. End sales pitch.

@@

\item[space-time leak] In a functional reactive service any particular element can depend on values that are far in the past. Clearly the longer the program is executing, the longer the history of events, or the longer the stream is. A longer stream takes up more memory and can cause slowdown if the stream is not trimmed after a certain point. Typically a garbage collection service of some kind is used to clean up old events that no longer being depended on. This is analogous to a memory leak in imperative programming. The value is said to be a space-time leak if it is unnessisarly being used for computations when it will have no affect on any current elements.
\end{description}
\section{Related work}
\subsection{High order streams}
\section{Future work}
Probably some since we want to keep working on things. I bet it will have to do with extending the language definition and possibly defining streams better.

\bibliography{paper.bib}{}
\bibliographystyle{plain}
\end{document}
